\documentclass[11pt]{article}

% Packages augment basic latex. Here I use the geometry package to change the margins.
\usepackage{geometry}  % give some flexibility to format
\geometry{verbose,tmargin=1.00in,bmargin=1.00in,lmargin=1.0in,rmargin=1.0in} % needs the package geometry to work

%For figures.
\usepackage{graphicx}

%This marks the start
\begin{document}

\title{Project Proposal}
\author{Dan Crankshaw, Dan Deutsch, Ryan Cotterell}

\maketitle

The goal of our project is to create an infinite mixture model using a Direchlet process
and Gibbs sampling to cluster Arabic social media data by dialect. This process will
have several steps.
\begin{itemize}
\item
We will begin with a literature review to understand the theoretical underpinnings
of mixture models, infinite mixture models, Dirichlet processes, and Gibbs sampling.
At the end of this we will create tutorial including sample code that will attempt
to explain these concepts to someone with only an undergraduate computer science
background.

\item We will then implement an Infinite Mixture Model (IMM) that uses a Dirichlet process
for the priors on the clusters and Gibbs sampling to perform inference. We will check
the implementation against a known data set to verify its correctness.

\item
We will also implement a finite mixture model and derive a Gibbs sampler for this model as well.
We will also test this implementation against a known data set.

\item
Finally, we will apply both the IMM and the FMM to a data set of short Arabic social media
messages (SMS's, tweets, etc) to cluster these messages by dialect.
\end{itemize}




\end{document}
